Without loss of generality, any reduced ring is a field

### 2018-04-10 slides-munich2018.tex
typo

\begin{frame}{Investigating the forcing model}
  \vspace*{-1em}
  \begin{varblockextra}{\textwidth}{}{
    \hil{Examples:} being local, reduced, an integral domain.
  }
    \justifying
    Assuming the Boolean prime ideal theorem, any first-order
    formula ``$\forall \ldots \forall\_ (\cdots \Longrightarrow \cdots\!\,)$'',
    where the two subformulas may not contain~``$\Rightarrow$'' and~``$\forall$'',
    holds for~$A^\sim$ iff it holds for all stalks~$A_\ppp$.
  \end{varblockextra}
  \pause
  \begin{align*}
    \intertext{The forcing model has additional \hil{unique properties}, e.\,g.\@}
    A &\models \forall x\?A^\sim\_ \neg(\speak{$x$ inv.}) \Rightarrow \speak{$x$ nilpotent} \\
    \intertext{which if~$A$ is reduced implies the \hil{field condition}}
    A &\models \forall x\?A^\sim\_ \neg(\speak{$x$ inv.}) \Rightarrow x = 0.
  \end{align*}
  \emph{Translation.} For any element~$x \in A$, if~$f = 0$ is the only element such
  that~$x$ is invertible in~$A[f^{-1}]$, then~$x = 0$.
\end{frame}

>>>>

\begin{frame}{Investigating the forcing model}
  \vspace*{-1em}
  \begin{varblockextra}{\textwidth}{}{
    \hil{Examples:} being local, reduced, an integral domain.
  }
    \justifying
    Assuming the Boolean prime ideal theorem, any first-order
    formula ``$\forall \ldots \forall\_ (\cdots \Longrightarrow \cdots\!\,)$'',
    where the two subformulas may not contain~``$\Rightarrow$'' and~``$\forall$'',
    holds for~$A^\sim$ iff it holds for all stalks~$A_\ppp$.
  \end{varblockextra}
  \pause
  \begin{align*}
    \intertext{The forcing model has additional \hil{unique properties}, e.\,g.\@}
    A &\models \forall x\?A^\sim\_ \neg(\speak{$x$ inv.}) \Longrightarrow \speak{$x$ nilpotent} \\
    \intertext{which if~$A$ is reduced implies the \hil{field condition}}
    A &\models \forall x\?A^\sim\_ \neg(\speak{$x$ inv.}) \Longrightarrow x = 0
    \quad\text{and also} \\
    A &\models \forall x\?A^\sim\_ \neg\neg(x = 0) \Longrightarrow x = 0.
  \end{align*}
  \emph{Translation.} For any element~$x \in A$, if~$f = 0$ is the only element such
  that~$x$ is invertible in~$A[f^{-1}]$, then~$x = 0$.
\end{frame}
